Msc Thesis Figures

### 2020-08-07 docs/msc_thesis_figures.Rmd
fix

non_forest <- final_all %>% 
  filter(type != "forest") %>% 
  mutate(value = as.factor(value), timestep = as.factor(timestep)) %>% 
  ggplot(aes(fill=timestep, y=area, x=new_class)) + 
  geom_bar(position="dodge", stat="identity") +
  scale_fill_manual(values = bi_colors) +
  theme(legend.position = "right") +
  facet_grid(~sce) +
  labs(x = "Land use Class", 
       y = "Mean Area (hectare)", 
       fill = "Year") +
  NULL

>>>>

non_forest <- final_all %>% 
  filter(type != "forest") %>% 
  filter(!(new_class %in% c("Water", "Wetlands", "Roads"))) %>% 
  mutate(value = as.factor(value), timestep = as.factor(timestep)) %>% 
  ggplot(aes(fill=timestep, y=area, x=new_class)) + 
  geom_bar(position="dodge", stat="identity") +
  scale_fill_manual(values = bi_colors) +
  theme(legend.position = "right") +
  facet_grid(~sce) +
  labs(x = "Land use Class", 
       y = "Mean Area (hectare)", 
       fill = "Year") +
  NULL
